Word learning at the semantics pragmatics interface

### 2020-04-20 paper/supplementary_material.Rmd
include knit to PDF

---
title: "Word learning at the semantics pragmatics interface"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

As a second step, we investigated how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a]. We pre-registered the use of default priors in all models. However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent. The priors we used were $\text{Gaussian}(0,5)$ for fixed (population level) effects and $\text{Cauchy}(0,1)$ for standard deviations of random effects. The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`. That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects). We did not pre-register agent as a random effect, but retrospecitvely included it to be consistent with Experiment 2 and 3.

@@

\begin{equation}
P_{L_1}(r \mid u)\propto P_{S_1}(u \mid r) \cdot P(r \mid \rho_i) \\ 
P_{S_1}(u \mid r)\propto P_{L_0}(r\mid u) ^{\alpha_i} \\
P_{L_0}(r\mid u) \propto \mathcal{L}(u, r \mid \theta_{ij})
(\#eq:rsabasic)
\end{equation}

@@

\begin{equation}
P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i) \\ 
P_{S_1}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P_{L_0}(r \mid u; \{\theta_{ij}\}) ^{\alpha_i} \\
P_{L_0}(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})
(\#eq:rsafull)
\end{equation}

@@

```{r fig4, include = T, fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity. Solid lines in show the MAP estimate for each parameter. Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty. (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1))
```
### Models

@@

\begin{equation}
P^{mixture}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i) \\
P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\}) \propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\})
(\#eq:mix)
\end{equation}

where $P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})$ represents a mutual-exclusivity inference from a listener with a uniform prior on referents. $P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}$ is the same as in Eq. \@ref(eq:rsafull) above.

@@

\begin{equation}
P^{dev\_mixture}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i) \cdot P(r \mid \rho_i) \\
(\#eq:devmix)
\end{equation}

>>>>

---
title: "Word learning at the semantics pragmatics interface"
subtitle: "Supplementary material"
author: "Manuel Bohn, Michael Henry Tessler, Megan Merrick and Michael C. Frank"
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\thetable}{S\arabic{table}} 
  \renewcommand{\thefigure}{S\arabic{figure}}
---

@@

As a second step, we investigated how the inference changed as a function of age and the familiar object. We modeled the trial by trial data using a Bayesian generalized linear mixed model (GLMM). We used the function `brm` from the package `brms` [@R-brms_a]. We pre-registered the use of default priors in all models. However, the model in Experiment 3 was unable to initialize with default priors and we thus used weakly informative priors for all models to be consistent. The priors we used were $\mathcal{N}(0,5)$ for fixed (population level) effects and $\text{Cauchy}(0,1)$ for standard deviations of random effects. The model formula was `correct ~ age + (1 | id) + (age | object) + (age | agent)`. That is, we modeled an overall slope for age (continuous, anchored at the minimum) and the object specific developmental trajectories as deviations from the overall intercept and slope (random effects). We did not pre-register agent as a random effect, but retrospecitvely included it to be consistent with Experiment 2 and 3.

@@

\begin{equation}
P_{L_1}(r \mid u)\propto P_{S_1}(u \mid r) \cdot P(r \mid \rho_i)
(\#eq:rsabasic1)
\end{equation}

\begin{equation}
P_{S_1}(u \mid r)\propto P_{L_0}(r\mid u) ^{\alpha_i}
(\#eq:rsabasic2)
\end{equation}

\begin{equation}
P_{L_0}(r\mid u) \propto \mathcal{L}(u, r \mid \theta_{ij})
(\#eq:rsabasic3)
\end{equation}

@@

\begin{equation}
P_{L_1}(r \mid u; \{\rho_i, \alpha_i\, \theta_{ij}\})\propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}) \cdot P(r \mid \rho_i)
(\#eq:rsafull1)
\end{equation}

\begin{equation}
P_{S_1}(u \mid r; \{\alpha_i\, \theta_{ij}\})\propto P_{L_0}(r \mid u; \{\theta_{ij}\}) ^{\alpha_i}
(\#eq:rsafull2)
\end{equation}

\begin{equation}
P_{L_0}(r \mid u; \{\theta_{ij}\}) \propto \mathcal{L}(u, r \mid \theta_{ij})
(\#eq:rsafull3)
\end{equation}

@@

```{r fig4, include = T, fig.cap = "Developmental trajectories for model parameters based on the posterior distribution for (A) semantic knowlede, (B) speaker informativeness and (C) prior sensitivity. Solid lines in show the MAP estimate for each parameter. Lighter lines in (B) and (C) show 300 random draws from the posterior distributon to visualize uncertainty. (A) does not include these random draws for the sake of clarity.", fig.width=12, fig.height = 4}
ggarrange(plot_sem_know, plot_speak_opt, plot_prior , labels = c("A","B","C"), nrow = 1, widths = c(1.3,1,1))
```

### Models

@@

\begin{equation}
P^{mixture}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)
(\#eq:mix1)
\end{equation}

\begin{equation}
P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\}) \propto P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\})
(\#eq:mix2)
\end{equation}

where $P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})$ represents a mutual-exclusivity inference from a listener with a uniform prior on referents. $P_{S_1}(u \mid r; \{\alpha_i, \theta_{ij}\}$ is the same as in Eq. \@ref(eq:rsafull2) above.

@@

\begin{equation}
P^{dev\_mixture}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i) \cdot P(r \mid \rho_i)
(\#eq:devmix)
\end{equation}
